The truncated KdV framework for modeling anomalous waves induced by abrupt depth changes

### 2019-08-02 paper2_JNLS/paper.tex
NM

The incoming waves are randomized and generated with a peak forcing frequency of $\freqp$, which gives rise to the following quantities
\begin{align}
&c = \sqrt{g \depth}
&&\mbox{\em local wave speed} \\
&\lam = c/\freqp = \sqrt{g \depth} / \freqp
&&\mbox{\em local peak wave length} \\
&\etastd = \mean{\eta^2}^{1/2} 
&&\mbox{\em surface displacement standard deviation} \\
\end{align}
where $\mean{\cdot}$ indicates the mean of a quantity. 
Note that the characteristic wave speed $c = c_{\pm}$ and wavelength $\lam = \lamupdn$ each take different values upstream and downstream of the ADC. We remark that experimental measurements indicate that $\etastd = \mean{\eta^2}^{1/2}$ is nearly the same on both values of the ADC. Hence, we will not distinguish between upstream and downstream values of $\etastd$.
%
See Table \ref{paramtable} for a summary of important parameters.

@@

With the above choices, the dimensionless KdV takes the form
\begin{align}
\label{dimlessKdV}
&u_t + C_3 \drat^{-3/2} \, u u_x + C_2 \drat^{1/2} \, u_{xxx} = 0
\qquad \text{for } x \in [-\pi,\pi] \\
&C_3 = \frac{3}{2} \pi^{3/2} \epsup \delup^{-1}  \\
&C_2 = \frac{\pi^3 \delup}{6 \lamfac^2} 
\end{align}
where dimensionless parameters are given by
\begin{align}
&\drat = {\depth}/{\dup} \, .
&&\mbox{\em dimensionless depth} \\
&\epsup = \etastd / \dup
&&\mbox{\em upstream amplitude-to-depth ratio} \\
&\delup = \dup / \lamup
&&\mbox{\em upstream depth-to-wavelength ratio}
\end{align}
While $\epsup$ and $\delup$ are fixed parameters, the dimensionless depth, $\drat = \dratupdn$, changes value across the ADC. Recall that the reference frame of \eqref{dimlessKdV} moves with the local wave speed via the variable $\xi = x-ct$ from \eqref{KdV}. Thus, the ADC is met at some time $T_{ADC}$, and for simplicity we set $T_{ADC} = 0$. Then the dimensionless coefficient $\drat$ is a piece-wise constant function of dimensionless time
\begin{equation}
\drat = 
\begin{cases}
1 		&\quad \mbox{for } \tilde{t}<0 \\
\dratdn = {\ddn}/{\dup} 	&\quad \mbox{for } \tilde{t}>0
\end{cases}
\end{equation}

>>>>

The incoming waves are randomized and generated with a peak forcing frequency of $\freqp$, which gives rise to the following quantities
\begin{align}
&c = \sqrt{g \depth}
&&\mbox{\em local wave speed} \\
&\lam = c/\freqp = \sqrt{g \depth} / \freqp
&&\mbox{\em local peak wave length} \\
&\etastd = \mean{\eta^2}^{1/2} 
&&\mbox{\em standard deviation of displacement} \\
\end{align}
where $\mean{\cdot}$ indicates the mean of a quantity. 
Note that the characteristic wave speed $c = c_{\pm}$ and wavelength $\lam = \lamupdn$ each take different values upstream and downstream of the ADC. We remark that experimental measurements indicate that $\etastd = \mean{\eta^2}^{1/2}$ is nearly the same on both values of the ADC. Hence, we will not distinguish between upstream and downstream values of $\etastd$.
%
See Table \ref{paramtable} for a summary of important parameters.

@@

With the above choices, the dimensionless KdV takes the form
\begin{align}
\label{dimlessKdV}
&u_t + C_3 \drat^{-3/2} \, u u_x + C_2 \drat^{1/2} \, u_{xxx} = 0
\qquad \text{for } x \in [-\pi,\pi] \\
&C_3 = \frac{3}{2} \pi^{3/2} \epsup \delup^{-1} \, , \quad
C_2 = \frac{\pi^3 \delup}{6 \lamfac^2} 
\end{align}
where dimensionless parameters are given by
\begin{align}
&\drat = {\depth}/{\dup} \, .
&&\mbox{\em dimensionless depth} \\
&\epsup = \etastd / \dup
&&\mbox{\em upstream amplitude-to-depth ratio} \\
&\delup = \dup / \lamup
&&\mbox{\em upstream depth-to-wavelength ratio}
\end{align}
While $\epsup$ and $\delup$ are fixed parameters, the dimensionless depth, $\drat = \dratupdn$, changes value across the ADC. Recall that the reference frame of \eqref{dimlessKdV} moves with the local wave speed via the variable $\xi = x-ct$ from \eqref{KdV}. Thus, the ADC is met at some time $T_{ADC}$, and for simplicity we set $T_{ADC} = 0$. Then the dimensionless coefficient $\drat$ is a piece-wise constant function of dimensionless time
\begin{equation}
\drat = 
\begin{cases}
1 		&\quad \mbox{for } \tilde{t}<0 \\
\dratdn = {\ddn}/{\dup} 	&\quad \mbox{for } \tilde{t}>0
\end{cases}
\end{equation}
